Canonical rings of $\bq$-divisors on Minimal Rational Surfaces

### 2015-07-31 surfaces-write-up/surface-write-up.tex
confused about i subscripts

\maketitle
\todo{Aaron: Standardize generation in degree ... phrasing. I like ``generation in degree at most.''\\
Peter: I prefer ``Generated in degrees at most'' (plural).}

@@

Aaron: Does $E_\mu$ depend on $i$? I thought it didn't, but if it does, then we should definitely do $E_{i,\mu}$ since I didn't
realize it depends on $i$. If $E_\mu$ doesn't depend on $i$, then we can just write $E_i$, and $E_\mu$,
and there is no danger of confusion because the subscripts live in different categories.
\\
Peter:  Yes, essentially everything in the remainder of this proof depends on $i$, e.g.: $\omega$, $\lambda$ (depends on $i$ as well as the choice of $r_{i,j}$'s), $E$, all $E_\mu$'s, $F$, $F_\mu$'s; I think that is everything.  I do not believe it would be helpful to add subscripts to all of these.  Instead maybe it would be better just to have one sentence that very clearly says everything in the following proof fixes $i$ and depends on $i$.
}
we simply write $f_i$ as a 
polynomial in $f_1, \ldots f_4$. Furthermore, these
generate all relations, since they allow us to reduce any $\prod_{j =
1}^n f_j^{c_j}$ to the canonical form where $r_i = - \lfloor d \alpha_i
\rfloor$ whenever $i > 4$.  To bound the degree of generation of these relations, we bound the degree of generation of the ideal $(z_i - \beta_i) \cap \ker(\psi)$ for each $i$.

@@

\todo{Is $\sigma = \omega$? If not I'm very confused, since I don't see $\sigma$ defined anywhere before or after
	but it seems like the key to the whole proof.
	\\
Peter: Oops, sorry, I changed some of the $\sigma$'s to $\omega$'s but clearly not all of them.  Maybe I should have used a macro...  I fixed the ones I saw, but let me know if you see any more $\sigma$'s popping up anywhere.
}
with $E$ of the form
\begin{equation}\label{eqn:hirz-E-translation}
	E = \begin{cases}
	\frac{1}{\kappa_i} e_i  	&  \mbox{ if }i\in \Te\\
	\sum_{j\in \Tm} r_{i,j} e_{i,j}: r_{i,j}\in \bq, \sum_{j\in \Tm} r_{i,j}\kappa_{i,j}' = 1 & \mbox{ if } i\in \Tp\\
	\sum_{j\in \Tp} r_{j,i} e_{j,i}: r_{j,i} \in \bq, \sum_{j\in \Tp} r_{j,i} \kappa_{i,j}'' = 1 	& \mbox{ if } i\in \Tm\\
	\end{cases}.
\end{equation}
Specifically, if we write out $\omega = \sum_{j\in \Te} s_j e_j + \sum_{j\in \Tp, k \in \Tp} s_{j,k} e_{j,k}$, then any choice of $r_{j,k}$'s not greater than the respective $s_{j,k}$'s such that $r_{i,j} \kappa_{i,j}' =1$ (when $i\in \Tp$ but a similar statement holds for $i\in \Tm$) will suffice.  Such a choice of $r_{i,j}$'s uniquely determines the necessary $\lambda$.

>>>>

\maketitle
\todo{Aaron: Standardize generation in degree ... phrasing. I like ``generation in degree at most.''\\
Peter: I prefer ``Generated in degrees at most'' (plural).

Aaron: What does plural mean here?
I was thinking of doing something along the lines of
$R$ is generated in degree at most $g$ with relations in degree at most $r$.}

@@

Aaron: Does $E_\mu$ depend on $i$? I thought it didn't, but if it does, then we should definitely do $E_{i,\mu}$ since I didn't
realize it depends on $i$. If $E_\mu$ doesn't depend on $i$, then we can just write $E_i$, and $E_\mu$,
and there is no danger of confusion because the subscripts live in different categories.
\\
Peter:  Yes, essentially everything in the remainder of this proof depends on $i$, e.g.: $\omega$, $\lambda$ (depends on $i$ as well as the choice of $r_{i,j}$'s), $E$, all $E_\mu$'s, $F$, $F_\mu$'s; I think that is everything.  I do not believe it would be helpful to add subscripts to all of these.  Instead maybe it would be better just to have one sentence that very clearly says everything in the following proof fixes $i$ and depends on $i$.

Aaron: How does $E_\mu$ depend on $i$? If you'd prefer to just say everything depends on $i$, I'm ok with it, though I still think including $i$ subscripts would be slightly
preferable. Perhaps just say near the beginning a list of all the things that will depend on $i$. I don't think you can say "everything for the remainder of the proof depends on i", because that's not true, e.g., $\ell_j$ for $j \neq i$ doesn't depend on $i$, though of course this is very confusing because you write $\ell_i$ in the definition of $\deg E$. (Won't this be more difficult than just writing a supscript or superscript $i$ though?)
}
we simply write $f_i$ as a 
polynomial in $f_1, \ldots f_4$. Furthermore, these
generate all relations, since they allow us to reduce any $\prod_{j =
1}^n f_j^{c_j}$ to the canonical form where $r_i = - \lfloor d \alpha_i
\rfloor$ whenever $i > 4$.  To bound the degree of generation of these relations, we bound the degree of generation of the ideal $(z_i - \beta_i) \cap \ker(\psi)$ for each $i$.

@@

\todo{Aaron:
Does $E$ depend on $\omega$? I.e. have we fixed an $\omega$ for the rest of the proof?
If so, why can we do this?
}
\todo{Aaron: If $i$ has been fixed for the remainder of the proof, why 
are we using $i$ as dummy subscripts everywhere?}
with $E$ of the form
\begin{equation}\label{eqn:hirz-E-translation}
	E = \begin{cases}
	\frac{1}{\kappa_i} e_i  	&  \mbox{ if }i\in \Te\\
	\sum_{j\in \Tm} r_{i,j} e_{i,j}: r_{i,j}\in \bq, \sum_{j\in \Tm} r_{i,j}\kappa_{i,j}' = 1 & \mbox{ if } i\in \Tp\\
	\sum_{j\in \Tp} r_{j,i} e_{j,i}: r_{j,i} \in \bq, \sum_{j\in \Tp} r_{j,i} \kappa_{i,j}'' = 1 	& \mbox{ if } i\in \Tm\\
	\end{cases}.
\end{equation}
Specifically, if we write out $\omega = \sum_{j\in \Te} s_j e_j + \sum_{j\in \Tp, k \in \Tp} s_{j,k} e_{j,k}$, then any choice of $r_{j,k}$'s not greater than the respective $s_{j,k}$'s such that $r_{i,j} \kappa_{i,j}' =1$ (when $i\in \Tp$ but a similar statement holds for $i\in \Tm$) will suffice.  Such a choice of $r_{i,j}$'s uniquely determines the necessary $\lambda$.
